
---
title: "RWorksheet_Ganon#1"
author: "Ganon, Andrew Vinz C."
date: "2024-09-17"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

1.
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41)

length(age)

age

```
2.
```{r}
reciprocal_age <- 1/ age

reciprocal_age
```

3. It generates a new vector. An extended version of the original age vector, with a 0 added in the middle.
```{r}
new_age <- c(age, 0, age)
```

4.
```{r}
sort_age <- sort(age)

sort_age
```

5.
```{r}
min_age <- min(age)
max_age <- max(age)
min_age
max_age
```

6.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)

length(data)

data
```

7.
```{r}
double_data <- data*2

double_data
```
A: "it will multiply into two"

8. Generate a sequence for the following scenario:

8.1

```{r}
seq_1_to_100 <- 1:100
```

8.2
```{r}
seq_20_to_60 <- 20:60
```

8.3
```{r}
mean_20_to_60 <-
mean(seq_20_to_60)
```

8.4
```{r}
sum_51_to_91 <- sum(51:91)
```

8.5
```{r}
seq_1_to_1000 <- 1:1000
```

a.
```{r}
numdatapoints <- length(seq_1_to_100) +
  length(seq_20_to_60) + 1 + 1

numdatapoints
```
b.
```{r}
seq_1_to_100; seq_20_to_60;
mean_20_to_60; sum_51_to_91
```
c.
```{r}
subset_data <-
seq_1_to_1000[seq_1_to_1000 <= 10]

max_value <- max(subset_data)

max_value
```

9.
```{r}
not_divisible <- Filter(function(i) { all(i %% c(3, 5, 7) != 0) }, seq(100))

not_divisible
```

10.
```{r}
seq_backwards <- seq(100, 1, by = -1)
```

11.
```{r}
multiples_3_or_5 <- Filter(function(x) {x %% 3 == 0 || x %% 5 == 0}, seq(1, 24))

sum_multiples <- sum(multiples_3_or_5)
```

a. 
```{r}
num_data_points_10_11 <- length(seq_backwards) + length(multiples_3_or_5)
```

b.
```{r}
seq_backwards; multiples_3_or_5; sum_multiples; num_data_points_10_11
```

12. Output will be an error, the variable x is used before it was assigned a value

13.
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)

score[2]

score[3]
```

14.
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
```
b. output displays the vector 'a' with NA values changed to "-999"

15. 
```{r}
name <- readline(prompt = "Input your name: ")

age <- readline(prompt = "Input your age: ")

print(paste("My name is",name, "and I am",age ,"years old."))

print(R.version.string)
```

The output shows a personalized message tailored to the user's input, followed by the current R version string.












