---
title: "RWorksheet_Ganon#4c.Rmd"
author: "Ganon, Andrew Vinz C."
date: "`r Sys.Date()`"
output: pdf_document
---

#1.
```{r}
library(readxl)
mpg <- read.csv("mpg.csv")
mpg
```
#a. first you need to upload and read the csv file using read.csv

#b. the variables that are categorical are manufacturer, trans, model, trans, drv, fl, and class.

#c. the continuous variables are disp, cty, and hwy

#2.
```{r}
manufacture_car <- table(mpg$manufacturer)
manufacture_car

```
# the most models are dodge which is 37. 

```{r}
model_car <- table(mpg$model)
model_car

# The caravan 2wd with 11 variations has the most.
```

# a. Group the manufacturers and find the unique models. Show your codes and result.

```{r}
library("dplyr")
unique_mod <- mpg %>%
 group_by(manufacturer) %>%
 summarise(models = n_distinct(model))
unique_mod
```

#b. Graph the result by using plot() and ggplot(). 
```{r}
library(ggplot2)
unique_mod$manufacturer <- as.factor(unique_mod$manufacturer)
unique_mod$models <- as.numeric(unique_mod$models)
```

```{r}
plot(unique_mod$manufacturer, unique_mod$models,
     type = "p",
     col = "orange",
     main = "Number of Unique Models per Manufacturer",
     xlab = "Manufacturer",
     ylab = "Unique Model Count",
     las = 3)
ggplot(unique_mod, aes(manufacturer, models), y = models) +
  geom_bar(stat = "identity", fill = "blue", color = "green") +
  labs(title = "Number of Unique Models per Manufacturer", x = "Manufacturer", y = "Unique Model Count")
```

# 2.
```{r}
library(ggplot2)
ggplot(unique_mod, aes(manufacturer, models), y = models) +
  geom_point( color = "gold")

# this had shown the representation of the data using point
# b. For you, is it useful? If not, how could you modify the data to make it more informative?

# This is quite useful, but if necessary, you can enhance it by transforming the data, summarizing it, using color to categorize, and exploring interactive tools.
```

#3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.
```{r}

top_mpg <- mpg %>%
  arrange(desc(mpg)) %>%
  head(20)
top_mpg
ggplot(top_mpg, aes(model,year)) + geom_point()
```
#4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}
car_counted <- mpg %>%
  group_by(model) %>%        
  summarise(count = n()) %>% 
  arrange(desc(count))     

# Display the result
car_counted
```
# a.  
```{r}
ggplot(car_counted, aes(x = model, y = count)) +
  geom_bar(stat = "identity", fill = "red", color = "blue") +
  labs(title = "Top 20 Observations", x = "Model", y = "Count of Cars")
```
#b. 
```{r}
ggplot(car_counted, aes(x = model, y = count)) +
  geom_bar(stat = "identity", fill = "red", color = "blue") +
  labs(title = "Top 20 Observations", x = "Model", y = "Count of Cars") +
  coord_flip()
```
#5.

```{r}
library("ggplot2")
ggplot(mpg, aes(x = displ, y = cyl, color = displ)) + geom_point(size = 3) +  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders (cyl)",
       y = "Engine Displacement (displ)")
```

#6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). 

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = cyl)) +
  geom_point(size = 3) +  
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement (displ)",
       y = "Highway MPG (hwy)")
```
# 6. Import the traffic.csv onto your R environment.
```{r}
traffic <- read.csv("traffic.csv")
```


```{r}
str(traffic)
# The dataset contains 48,120 observations and 4 variables: DateTime, Junction, Vehicles, and ID.
```
# b. subset the traffic dataset into junctions. What is the R codes and its output?
```{r}
junction <- split(traffic, traffic$Junction)

```
# c. Plot each junction in a using geom_line(). Show your solution and output.
```{r, error=TRUE}
traffic$DateTime <- as.POSIXct(traffic$DateTime, format = "%Y-%m-%d %H:%M:%S")

# Plot each junction using geom_line() and facet_wrap()
ggplot(traffic, aes(x = DateTime, y = Vehicles)) +
  geom_line(color = "blue") +
  labs(title = "Traffic Volume Over Time at Each Junction",
       x = "DateTime",
       y = "Number of Vehicles") +
  facet_wrap(~ Junction)  

```
# 7.
```{r}
alexa <- read.csv("alexa_file.csv")
```
```{r}
str(alexa)
ncol(alexa)
# There are 3150 observations and 5 columns in alexafile

```
#b. group the variations and get the total of each variations. Use the dplyr package. Show solution and answer.
```{r}
print(colnames(alexa))

variation_totals <- alexa %>%
 group_by(variation) %>%
  summarise(total = n())
variation_totals
```
# c. 
```{r}
library("ggplot2")
ggplot(alexa, aes(x = date, y = variation)) +
geom_point() + labs(title = "Variations over Time", x = "Date", y = "Variation", color = "Verified")
```
# d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the graphs. Show your answer and solution.
```{r}

alexa$date <- as.Date(alexa$date, format = "%d-%b-%y")
review_counts <- alexa %>%
  group_by(date) %>%
  summarise(review_count = n())
ggplot(data = review_counts, aes(x = date, y = review_count)) +
  geom_line(color = "blue", size = 1) +
  labs(
    title = "Number of Verified Reviews Over Time",
    x = "Date",
    y = "Number of Verified Reviews"
  ) +
  theme_minimal()
```
#e. 
```{r}
variation_ratings <- alexa %>%
  group_by(variation) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE)) %>%
  arrange(desc(average_rating))


ggplot(variation_ratings, aes(x = reorder(variation, -average_rating), y = average_rating)) +
  geom_bar(stat = "identity", fill = "gold") +
  coord_flip() +  # Flip coordinates for better readability
  labs(title = "Average Rating by Product Variation",
       x = "Product Variation",
       y = "Average Rating") +
  theme_minimal()
```





